Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-01 doc/RMD/table-1.Rmd
use the correct flags this time :see_no_evil:
change table 1 to be more concise
I changed table 1 so that it highlights the salient features of
our data.

```{r load_packages, warnings = FALSE, messages = FALSE}
library("readr")
library("dplyr")
library("huxtable")
```

@@

dat <- readr::read_csv(file.path(PROJHOME, "data/clean_data.csv"), col_types = clmn) %>%
  mutate(Country = ifelse(nchar(Region) == 2, "USA", Region)) %>% # Defining country column
  mutate(Region = ifelse(nchar(Region) == 2, Region, "-")) %>%     # Adding blanks for international "states"
  select(Country, Region, Source, Year, Host) %>%                 # Summarizing the number of isolates
  group_by_all() %>%                                              #
  summarize(N = n()) %>%                                          #
  arrange(desc(Country), Region, Source, Year) %>%                # Rearranging rows
  group_by(Country, Region, Source) %>%                           # Collapsing Years and Hosts
  summarize(Year = paste(sort(unique(Year)), collapse = ", "),    #
            Host = paste(sort(unique(Host)), collapse = ", "),    #
            N = sum(N)) %>%                                       #
  arrange(desc(Country), Region, desc(N)) %>%                     # Rearranging rows
  group_by(Country, Region) %>%                                   # Adding blanks in repeated Country and Region Names
  mutate(set_blank = blank_it(Region)) %>%                        #
  ungroup() %>%                                                   #
  mutate(Country = ifelse(set_blank, "", Country)) %>%            #
  mutate(Region = ifelse(set_blank, "", Region)) %>%              #
  select(Country, Region, Source, Year, Host, N) %>%              #
  rename(State = Region) %>%                                      # Renaming columns
  rename(`Field Code` = Source)                                   #

>>>>

```{r load_packages, warning = FALSE, message = FALSE}
library("readr")
library("dplyr")
library("huxtable")
```

@@

dat <- readr::read_csv(file.path(PROJHOME, "data/clean_data.csv"), col_types = clmn) %>%
  mutate(Country = ifelse(nchar(Region) == 2, "USA", Region)) %>% # Defining country column
  mutate(Region = ifelse(nchar(Region) == 2, Region, "-")) %>%    # Adding blanks for international "states"
  mutate(Source = ifelse(Source == "wmn", "wmn", "producer")) %>% # Changing fields to binary counts
  select(Country, Region, Source, Year, Host) %>%                 # Summarizing the number of isolates
  group_by_all() %>%                                              #
  summarize(N = n()) %>%                                          #
  arrange(desc(Country), Region, Source, Year) %>%                # Rearranging rows
  group_by(Country, Region, Source) %>%                           # Collapsing Years and Hosts
  summarize(Year = paste(sort(unique(Year)), collapse = ", "),    #
            Host = paste(sort(unique(Host)), collapse = ", "),    #
            N = sum(N)) %>%                                       #
  arrange(desc(Country), Region, desc(N)) %>%                     # Rearranging rows
  group_by(Country, Region) %>%                                   # Adding blanks in repeated Country and Region Names
  mutate(set_blank = blank_it(Region)) %>%                        #
  ungroup() %>%                                                   #
  mutate(Country = ifelse(set_blank, "", Country)) %>%            #
  mutate(Region = ifelse(set_blank, "", Region)) %>%              #
  select(Country, Region, Source, Year, Host, N) %>%              #
  rename(State = Region) %>%                                      # Renaming columns
  rename(`Field Code` = Source)                                   #

### 2017-08-01 doc/manuscript/manuscript.Rmd
change table 1 to be more concise
I changed table 1 so that it highlights the salient features of
our data.

USA       CO     gree              2007, 2010 Pinto, Yellow                14

                 luc               2007, 2010 Yellow                       14

                 eat               2007, 2010 Yellow                       13

@@

USA       ID     unk                     2003 GH                            1

USA       MI     wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,          
                                              G122, ion, PO7863, WM31

                 tuc               2008, 2009 Black, Fuji, Vista            6

                 hur               2008, 2009 BL, Black, SR06233, Vista     5

                 sanc                    2008 Merlot                        3

                 unk               2003, 2009 GH, unk                       2

                 eln                     2009 unk                           1

                 mung                    2009 Zorro                         1

                 Sebewaing               2009 Black                         1

@@

USA       ND     rrv                     2007 unk                          21

                 gfc               2007, 2010 unk                           9

                 tlc                     2010 unk                           9

                 pmc                     2010 unk                           7

@@

                 wlc                     2010 unk                           4

                 stc                     2010 unk                           2

                 nec                     2010 unk                           1

@@

                 mtc               2007, 2010 Beryl, Emerson, Orion        12

                 sbf               2007, 2009 Beryl, Pinto, Weihing         6

                 unk                     2003 GH                            2

USA       NY     unk                     2003 GH                            1

@@

                 corv                    2003 G122                          1

                 unk                     2003 GH                            1

USA       WA     wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008  cornell, G122, Orion,          
                                              PO7104, PO7863, WM31

                 prsr                    2007 Merlot, Pinto, redkid        22

                 unk                     2003 GH                            1

USA       WI     dfor                    2003 GH                            1

                 unk                     2003 GH                            1

@@

                 flds                    2012 unk                           4

@@

                 vic                     2004 Beryl                         2

@@

Table: (\#tab:isolate-table) Description of *Sclerotinia sclerotiorum* isolates used in this study.
N = Number of Isolates. 
Key abbreviations: wmn = white mold screening nursery, unk = unknown.

>>>>

USA       CO     producer          2007, 2010 Pinto, Yellow                41

@@

USA       ID     producer                2003 GH                            1

USA       MI     wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,       
                                              G122, Orion, PO7863, WM31

                 producer    2003, 2008, 2009 BL, Black, Fuji, GH,         19 
                                              Merlot, SR06233, unk,        
                                              Vista, Zorro

@@

USA       ND     producer          2007, 2010 unk                          53

@@

@@

                 producer   2003, 2007, 2009, Beryl, Emerson, GH, Orion,   20 
                                         2010  Pinto, Weihing

USA       NY     producer                2003 GH                            1

@@

                 producer                2003 G122, GH                      2

USA       WA     wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008  cornell, G122, Orion, PO7      
                                              104, PO7863, WM31

                 producer          2003, 2007 GH, Merlot, Pinto, redkid    23

USA       WI     producer                2003 GH                            2

@@

                 producer                2012 unk                           4

@@

                 producer                2004 Beryl                         2

@@

Table: (\#tab:isolate-table) Description of *Sclerotinia sclerotiorum* isolates used in this study.
N = Number of Isolates. 
Key abbreviations: wmn = white mold screening nursery, producer = producer field, unk = unknown cultivar.
